\documentclass[defaultstyle,11pt]{thesis}% this is file mythesis.tex
\usepackage{latexsym} % to get LASY symbols
\usepackage{epsfig} % to insert PostScript figures
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\title{Application of Microphotoluminescence Spectroscopy to Study Semiconductor Quantum Well Disorder.}
\author{M.~W.}{Day}
\degree{Bachelor of Science} % #1 {long descr.}
 {B.S. } % #2 {short descr.}
 \otherdegrees{}
\dept{Department of}{Physics}
\advisor{Prof.}{Steven Cundiff}
\reader{Prof.~Rachel Goddard} % 2nd person to sign thesis
\readerThree{Ms.~Thora Nea} % 3rd person to sign thesis
\abstract{ \OnePageChapter Manufacturing processes unintentionally introduce fluctuations in the width of semiconductor quantum wells. These fluctuations subtly modulate the optical emission energies of exitons confined within the quantum well layer. It is therefore imperative to quantify these width fluctuations so their effect on exiton confinement potentials can be accounted for in ultrafast spectroscopic studies of semiconductor quantum wells. The use of micro-photoluminescence spectroscopy makes quantifying this disorder possible. I present microphotoluminesence spectroscopy work taken in pursuit of an Honors' thesis.}
\dedication[Dedication]{To the wonderful people in my life: family and friends alike.}
\acknowledgements{I'd like to sincerely thank Professor Steven Cundiff for years of tutelage. Without his guidance, I would not have been able to complete this thesis.}
 \ToCisShort % Table of Contents is *2* pages long
 \emptyLoT
\LoFisShort % one-page List of Figures
 
\begin{document}

\input chapter1.tex

\end{document}